Spectral Deferred Corrections Scheme for Low Mach Number Flows

### 2019-12-14 MAESTROeX_II/paper.tex
add Don -- he's been doing all the SDC interface work
add ref

@@

An alternate approach to advancing the thermodynamic variables is to use
spectral deferred corrections (SDC). SDC is an iterative scheme used to couple the various processes
together, with each process seeing an  approximation of the other processes as a source term.
The SDC algorithm converges to an integral representation of the solution in
time that couples all of the processes together in a self-consistent fashion.
It has been shown to be more accurate and efficient than Strang splitting in a
terrestrial, non-stratified, low Mach number reacting flow solver \cite{nonaka2012sdc},
so we believe an SDC version of MAESTROeX would greatly improve the efficiency of the code.
\\

>>>>

\author[0000-0003-2300-5165]{Donald Willcox}
\affiliation{Lawrence Berkeley National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

@@

An alternate approach to advancing the thermodynamic variables is to use
spectral deferred corrections (SDC). SDC is an iterative scheme used to couple the various processes
together, with each process seeing an  approximation of the other processes as a source term.
The SDC algorithm converges to an integral representation of the solution in
time that couples all of the processes together in a self-consistent fashion.
It has been shown to be more accurate and efficient than Strang splitting in a
terrestrial, non-stratified, low Mach number reacting flow solver \cite{nonaka2012sdc}.
SDC methods have also been demonstrated for compressible astrophysical flows \cite{castro_sdc}.
Based on this past work, we believe an SDC version of MAESTROeX would greatly improve the efficiency of the code.
\\
